High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-09-24 notebooks/fmnist.qmd

```{julia}
# Model parameters:
epochs = 10
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 512
activation = Flux.relu
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    # Dense(n_hidden, n_hidden, activation),
    # Dense(n_hidden, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                  # number of models in ensemble
_loss = Flux.Losses.logitcrossentropy       # loss function
_finaliser = x -> x                         # finaliser function
```

```{julia}
# Simple MLP:
mlp = NeuralNetworkClassifier(
    builder=builder, 
    epochs=epochs,
    batch_size=batch_size,
    finaliser=_finaliser,
    loss=_loss,
)

>>>>

```{julia}
# Model parameters:
epochs = 10
batch_size = minimum([Int(round(n_obs/10)), 128])
n_hidden = 512
activation = Flux.relu
builder = MLJFlux.@builder Flux.Chain(
    Dense(n_in, n_hidden, activation),
    # Dense(n_hidden, n_hidden, activation),
    # Dense(n_hidden, n_hidden, activation),
    Dense(n_hidden, n_out),
)
n_ens = 5                                  # number of models in ensemble
_loss = Flux.Losses.logitcrossentropy       # loss function
_finaliser = x -> x                         # finalizer function
```

```{julia}
# Simple MLP:
mlp = NeuralNetworkClassifier(
    builder=builder, 
    epochs=epochs,
    batch_size=batch_size,
    finalizer=_finaliser,
    loss=_loss,
)

### 2023-09-24 notebooks/gmsc.qmd

    function boxcox(x)
        transf = MLJ.UnivariateBoxCoxTransformer()
        x = exp.(x)
        mach = machine(transf, x)
        fit!(mach)
        z = MLJ.transform(mach, x)
        return z
    end
    Xmat = reduce(hcat, map(x -> boxcox(x), eachcol(Xmat)))
    X = table(Float32.(Xmat))
end
```

>>>>

    function boxcox(x)
        transf = MLJ.UnivariateBoxCoxTransformer()
        x = exper.(x)
        mach = machine(transf, x)
        fit!(mach)
        z = MLJ.transform(mach, x)
        return z
    end
    Xmat = reduce(hcat, map(x -> boxcox(x), eachcol(Xmat)))
    X = table(Float32.(Xmat))
end
```

### 2023-09-24 notebooks/poc.qmd

```{julia}
𝒟x = Normal()
𝒟y = Categorical(ones(2) ./ 2)
sampler = ConditionalSampler(𝒟x, 𝒟y, input_size=size(X)[1:end-1], batch_size=50)
n_hidden = 16
clf = JointEnergyClassifier(
    sampler;
    builder=MLJFlux.MLP(
        hidden=(n_hidden, n_hidden, n_hidden), 
        σ=Flux.swish
    ),
    batch_size=batch_size,
    finaliser=Flux.softmax,
    loss=Flux.Losses.crossentropy,
    jem_training_params=(
        α=[1.0,1.0,1e-1],
        verbosity=10,
    ),
    epochs=epochs,
    sampling_steps=30,
)
```

>>>>

```{julia}
𝒟x = Normal()
𝒟y = Categorical(ones(2) ./ 2)
sampler = ConditionalSampler(𝒟x, 𝒟y, input_size=size(X)[1:end-1], batch_size=50)
n_hidden = 16
clf = JointEnergyClassifier(
    sampler;
    builder=MLJFlux.MLP(
        hidden=(n_hidden, n_hidden, n_hidden), 
        σ=Flux.swish
    ),
    batch_size=batch_size,
    finalizer=Flux.softmax,
    loss=Flux.Losses.crossentropy,
    jem_training_params=(
        α=[1.0,1.0,1e-1],
        verbosity=10,
    ),
    epochs=epochs,
    sampling_steps=30,
)
```
